### 2011-02-10 paper/conclusion.tex

HyperNEAT produced higher-performing gaits than all of the parameterized
methods, with a max of 45.7 body lengths per minute, which is nearly 9 times the speed of the hand-coded gait.  This could be because HyperNEAT tends to generate coordinated gaits~\cite{clune2011performance, clune2009evolving}, allowing it to
take advantage of the symmetries of the problem, but can also explore a much larger space of possibilities than the
more restrictive 5-dimensional parameterized space.  HyperNEAT gaits tended to produce more complex sequences of motor commands, with different frequencies and degrees of coordination, whereas the
parameterized gaits were restricted to scaling single-frequency sine waves and could only produce certain types of motor regularities.

>>>>

HyperNEAT produced higher-performing gaits than all of the parameterized
methods. Its best-performing gait traveled 45.7 body lengths per minute, which is nearly 9 times the speed of the hand-coded gait.  This could be because HyperNEAT tends to generate coordinated gaits~\cite{clune2011performance, clune2009evolving}, allowing it to
take advantage of the symmetries of the problem, but can also explore a much larger space of possibilities than the
more restrictive 5-dimensional parameterized space.  HyperNEAT gaits tended to produce more complex sequences of motor commands, with different frequencies and degrees of coordination, whereas the
parameterized gaits were restricted to scaling single-frequency sine waves and could only produce certain types of motor regularities.

### 2011-02-10 paper/results.tex

One reason the randomly-generated SineModel5 gaits were so effective
may have been due to the SineModel5's bias toward regular, symmetric
gaits.  This may have allowed the random strategy --- focusing on
exploration --- to be competitive with the more directed strategies
that exploit information from past runs.

>>>>

One reason the randomly-generated SineModel5 gaits were so effective
may have been due to the SineModel5's bias toward regular, symmetric
gaits.  This may have allowed the random strategy --- focusing on
exploration --- to be competitive with the more directed strategies
that exploit information from past evaluations.
